---
title: "VRCC Analysis Pipeline"
author: "AM, FK, PM"
date: "May 5, 2019"
# contact: "klotzsche@cbs.mpg.de", "aleksander.molak@gmail.com"
output: html_document
chunk_output_type: console
self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
basic_color <- '#195e8c'
```

# Import libraries & setup directories

```{r message=FALSE, warning=FALSE}

# Utils
library(dplyr)
library(here)
library(haven)
library(readr)
library(tibble)
library(purrr)

# Plotting and tables
library(ggplot2)
library(sjPlot)

# Statistical tools
library(lme4)
library(lmtest)
library(lmerTest)
library(car)
library(BayesFactor)

# Load helper functions
source(here("./Code/Analyses/VRTask/Utils/get_cardio_info.R"))
source(here("./Code/Analyses/VRTask/Utils/read_utils.r"))

```

<br>

# Build the dataset

```{r warning=FALSE}

# Set up the data directory
VRCC_dir <- here()
data_dir <- here("Data/VRTask/Logfiles/ExpSubjects")

# Build the dataset
fulldata <- build_dataset(data_dir)

```

<br>

# Apply further transformations and create additional variables

```{r}

# Drop unused levels
fulldata <- droplevels(fulldata)

```

<br>

* ### Compute distance errors

```{r}

# Compute distance errors & add to the dataset
fulldata <- fulldata %>% 
  mutate(DistanceError = (EstimatedDistance - RealDistance),
         DistanceErrorAbs = abs(DistanceError),
         DistanceErrorNorm = DistanceError / RealDistance,
         DistanceErrorNormAbs = abs(DistanceErrorNorm)) %>% 
  mutate(totTrial = Trial + (Round - 1) * max(Trial))          # **AM 05-05-19**: What's that?
                                                               # **FK 07-07-19**: Labels the trials with sequential numbers over the whole experiment (1-720)   


```

<br>

* ### Add cardio information to the dataset

```{r warning=FALSE}

subjects_list <- fulldata %>%
                  select(ID) %>%
                  distinct()

cardio_data   <- NULL

for (subject in subjects_list$ID) {                               
  cardio_temp <- get_cardio_info(fulldata, subject)
  cardio_data <- bind_rows(cardio_data, cardio_temp)
}

# Join the data
fulldata <- full_join(fulldata, cardio_data)                 

```

<br>

# Main analysis

<br>

* ### Check if the distance error ($DE$) differs between threatning and non-threatning trials

```{r message=FALSE}

# Check the distribution of DE
ggplot(fulldata, aes(x = DistanceError, fill = FearObject)) + 
                           geom_histogram(alpha = .7) + 
                           xlab('Distance Error') + 
                           ylab('Value') + 
                           theme_minimal()

qqPlot(fulldata$DistanceError)

shapiro.test(fulldata$DistanceError)

```

<br>

## Testing the main hypothesis (1)

* ### Using two-tailed paired t-test and / or Wilcoxon paired test.

<br>

```{r}
# Split the data
fear_true <- fulldata %>% 
              filter(FearObject == 'True') %>%
              select(DistanceError) %>% pull

fear_flse <- fulldata %>% 
              filter(FearObject == 'False') %>%
              select(DistanceError) %>% pull

# Perform paired t-test
t.test(fear_true, fear_flse, paired = T)

# Perfom Wilcoxon signed-rank test
wilcox.test(fear_true, fear_flse, paired = T)

```

<br>

* ### Using bayesian t-test (BF).

<br>

```{r}
ttestBF(fear_true, fear_flse, paired = T)
```

<br>

## Testing the main hypothesis (2a) using multilevel modeling

```{r}
print('Implement this...')

```

<br>

# Exploratory / additional analyses

```{r}

mean_error_per_fear <- fulldata %>%
                          group_by(FearObject) %>%
                            summarise(MeanDistanceError = mean(DistanceError, na.rm=T),
                                      MeanDistanceErrorNorm = mean(DistanceErrorNorm, na.rm=T),
                                      MeanDistanceErrorAbs = mean(DistanceErrorAbs, na.rm=T))

mean_error_per_animal <- fulldata %>%
                          group_by(Stimulus) %>%
                            summarise(MeanDistanceError = mean(DistanceError, na.rm=T),
                                      MeanDistanceErrorNorm = mean(DistanceErrorNorm, na.rm=T),
                                      MeanDistanceErrorAbs = mean(DistanceErrorAbs, na.rm=T))
# 
# mean_dist_per_fear
# mean_dist_per_animal
      
```

