---
title: "VRCC - preliminary circular"
author: "AM, FK, PM"
date: "April 22, 2021"
# contact: "klotzsche@cbs.mpg.de", "aleksander.molak@gmail.com", "pawel.motyka@psych.uw.edu.pl"
output: html_document
chunk_output_type: console
self_contained: no
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
basic_color <- '#195e8c'
```

```{r}
setwd('C:\\Users\\aleksander.molak\\Documents\\Personal\\Fear from  heart - Central Kollegs\\centralkollegs18')
```

# Import libraries & setup directories & read the data

```{r message=FALSE, warning=FALSE}

# Utils
library(dplyr) 
library(here)
library(tidyr)

# Plotting and tables
library(ggplot2)
library(sjPlot)
library(gghalves)

# Statistical tools
library(lme4)
library(lmtest)
library(lmerTest)
library(car)
library(effsize)
library(psych)
library(performance)

source(here("./Code/Analyses/VRTask/Utils/stats_utils.r"))


# Set up the fulldata directory
VRCC_dir         <- here()
# Read the preprocessed data
data <- read.csv(file = paste0(VRCC_dir,"/Data/VRTask/VRCC_data_consolidated"))


```


## Compute and add circular components

### NOTE: Code in this notebook is based on the assumption that `relPosRRrad` is the varibale representing `CP` from the pre-reg document. Is this correct, Paweł?

```{r}
# Get circular components
rel_pos_circular <- get_circular_components(data$relPosRRrad, 2 * pi)

# Add them to df
data$relPosRRradCircCos <- rel_pos_circular$cos_component
data$relPosRRradCircSin <- rel_pos_circular$sin_component
```

## Model

According to the pre-reg document, we define the model as follows:

`DE ~ CP*Threat + (1 + r_true | ID)`

```{r}
# Specify data of interest
# d <- data[data$c_phase == "systole" | data$c_phase == "diastole",]

## Preregistered models:
# Null model
null_model <- lmer(DistanceError ~ 1 + (1 + RealDistance|ID), data = data)
summary(null_model)

# Full model
full_model <- lmer(DistanceError ~ relPosRRradCircCos * FearObject + relPosRRradCircSin * FearObject + (1 + RealDistance|ID), data = data)
summary(full_model)
plot_model(full_model, type = "int", mdrt.values = "meansd")
get_r2_mlm(full_model)

```

```{r}
anova(null_model, full_model)
```

## Prep a short pres on circular
## Fit loess per participant + embedd + embedd mean over all participants
## Add model diagnostics! [AM]
