---
title: <font size="5">**VRCC -- exploratory analysis **</font> 
author: <br> <font size="4"> Pawel Motyka, Felix Klotzsche, Aleksander Molak </font> <br>  *pmotyka@psych.pan.pl*  *klotzsche@cbs.mpg.de* *aleksander.molak@gmail.com*
date: <font size="3"> April 2021  </font>
output: html_document
chunk_output_type: console
self_contained: no

--- 

&nbsp;
<font size="4">
**List of sections**:

- [S1](#S1) – Load required packages and data
- [S2](#S2) - Comparison of localization error between cardiac phases
- [S3](#S3) - RR interval length and distance estimates
- [S4](#S4) - Animal assessment - threat, disgust, and speed ratings
- [S5](#S5) - Distance error as a function of subjective threat
- [S6](#S6) - Distance error as a function of anxiety levels, disgust, and speed ratings
- [S7](#S7) - Cybersickness (SSQ) and presence in VR (SUS)
- [S8](#S8) - Distance errors as a function of real distance
- [S9](#S9) - Distribution of stimulus onsets across the cardiac cycle


<a name="S1"></a>
&nbsp;

**1. Load required packages and data** 

```{r message=FALSE, warning=FALSE}

# Utils
library(dplyr) 
library(here)
library(tidyr)
source(here("./Code/Analyses/VRTask/Utils/stats_utils.r"))

# Plotting and tables
library(ggplot2)
library(sjPlot)
library(gghalves)
library(colorspace)

# Statistical tools
library(lme4)
library(lmtest)
library(lmerTest)
library(car)
library(effsize)
library(psych)
library(Rmisc)
library(afex)
library(circular) 

# Set up the fulldata directory
VRCC_dir  <- here::here()

# read behavioral & ecg data
data <- read.csv(file = paste0(VRCC_dir,"/Data/VRTask/VRCC_data_consolidated-2023-08-10.csv"))

# read intial ratings data
d_sub_start <- read.csv(file = paste0(VRCC_dir,"/Data/VRTask/Ratings/VRCC_data_initial_subjective_ratings.csv"))

# read mid-experimental ratings data
d_sub_mid <- read.csv(file = paste0(VRCC_dir,"/Data/VRTask/Ratings/VRCC_data_mid-experimental_subjective_ratings.csv"))
d_sub_mid$threat[d_sub_mid$threat == 0] <- NA # add NAs

# read questionnaires data
d_qstn <- read.csv(file = paste0(VRCC_dir,"/Data/VRTask/Ratings/VRCC_data_questionnaires.csv"))

# conversion of distance from m to cm
data <- data %>%
mutate(EstimatedDistance = EstimatedDistance * 100, RealDistance = RealDistance * 100, DistanceError = DistanceError * 100 , DistanceErrorAbs = DistanceErrorAbs * 100, LocalizationError = LocalizationError * 100)

```

<a name="S2"></a>
&nbsp;

**2. Comparison of localization error between cardiac phases** 

```{r}

# Localization error

d <- data[data$c_phase == "systole" | data$c_phase == "diastole",]

d <- dplyr::select(d, ID, LocalizationError, c_phase)
d <- d %>% dplyr::group_by(ID, c_phase)  %>% dplyr::summarize(LocalizationError = mean(LocalizationError))

d <- pivot_wider(d, names_from = c(c_phase), values_from = LocalizationError)

# perform t-test
shapiro.test(d$diastole)
shapiro.test(d$systole)
describe(d$diastole)
describe(d$systole)
wilcox.test(d$systole, d$diastole, paired = T)
#boxplot(d$systole, d$diastole, names = c("Systole", "Diastole"), ylim = c(0,1))
```

<a name="S3"></a>
&nbsp;

**3. RR interval length and distance estimates** 

```{r}

### 3.1 RR interval - distance & localization errors

d <- dplyr::select(data, ID, DistanceError, LocalizationError, RRLength)
d <- d %>% dplyr::group_by(ID) %>% dplyr::summarize(LocalizationError = mean(LocalizationError), DistanceError = mean(DistanceError), RRLength = mean(RRLength))

shapiro.test(d$LocalizationError)
shapiro.test(d$DistanceError)
shapiro.test(d$RRLength)

cor.test(d$RRLength, d$DistanceError, method = "pearson")
cor.test(d$RRLength, d$LocalizationError, method = "spearman")

```


<a name="S4"></a>
&nbsp;

**4. Animal assessment - threat, disgust, and speed ratings** 

```{r}

###. 4.1. Separate groups (threat, disgust, speed ratings)

di <- d_sub_start
di <- di %>% dplyr::group_by(ID, fear_object) %>% dplyr::summarize(threat = mean(threat), disgust = mean(disgust), speed = mean(how_fast))
di <- pivot_wider(di, names_from = c(fear_object), values_from = c(threat, disgust, speed))

# threat
shapiro.test(di$threat_False)
shapiro.test(di$threat_True)
wilcox.test(di$threat_True, di$threat_False, paired = T,  alternative = "two.sided", exact = F)
describe(di$threat_False)
describe(di$threat_True)

# disgust
shapiro.test(di$disgust_False)
shapiro.test(di$disgust_True)
wilcox.test(di$disgust_True, di$disgust_False, paired = T,  alternative = "two.sided", exact = F)
describe(di$disgust_False)
describe(di$disgust_True)

# speed
shapiro.test(di$speed_False)
shapiro.test(di$speed_True)
t.test(di$speed_True, di$speed_False, paired = T,  alternative = "two.sided")
describe(di$speed_False)
describe(di$speed_True)


###. 4.2. Invididual animals (threat, disgust, speed)

di <- d_sub_start
di <- di %>% dplyr::group_by(ID, Stimulus) %>% dplyr::summarize(threat = mean(threat), disgust = mean(disgust), speed = mean(how_fast))

dis <- pivot_wider(di, names_from = c(Stimulus), values_from = c(threat, disgust, speed))

cR <- rgb(178/255, 31/255, 0/255)
cB <- rgb(10/255, 80/255, 200/255)

# threat
boxplot(dis$threat_Crocodile, dis$threat_FinalWolf, dis$threat_FinalSnake, dis$threat_Scorpio, dis$threat_Deer, dis$threat_Pig,  dis$threat_Turtle, dis$threat_Rabbit, col = c(cR, cR, cR, cR, cB, cB, cB,cB), names = c("Crocodile", "Wolf", "Snake", "Scorpio", "Deer", "Pig", "Turtle", "Rabbit"), frame = FALSE, notch = F, ylab = "Subjective threat", cex.lab = 1.2, cex.axis = 1, ylim = c(1,7))
abline(h=0, col="gray20", lwd = 1.3, lty = 2)

points(c(mean(dis$threat_Crocodile, na.rm = T), mean(dis$threat_FinalWolf, na.rm = T), mean(dis$threat_FinalSnake, na.rm = T), mean(dis$threat_Scorpio, na.rm = T), mean(dis$threat_Deer, na.rm = T),mean(dis$threat_Pig, na.rm = T),mean(dis$threat_Turtle, na.rm = T),mean(dis$threat_Rabbit, na.rm = T)), pch = 19, cex = 1.4)
# export 3.5 x 7 cm

# disgust
boxplot(dis$disgust_Crocodile, dis$disgust_FinalWolf, dis$disgust_FinalSnake, dis$disgust_Scorpio, dis$disgust_Deer, dis$disgust_Pig,  dis$disgust_Turtle, dis$disgust_Rabbit, col = c(cR, cR, cR, cR, cB, cB, cB,cB), names = c("Crocodile", "Wolf", "Snake", "Scorpio", "Deer", "Pig", "Turtle", "Rabbit"), frame = FALSE, notch = F, ylab = "Subjective disgust", cex.lab = 1.2, cex.axis = 1, ylim = c(1,7))
abline(h=0, col="gray20", lwd = 1.3, lty = 2)

points(c(mean(dis$disgust_Crocodile, na.rm = T), mean(dis$disgust_FinalWolf, na.rm = T), mean(dis$disgust_FinalSnake, na.rm = T), mean(dis$disgust_Scorpio, na.rm = T), mean(dis$disgust_Deer, na.rm = T),mean(dis$disgust_Pig, na.rm = T),mean(dis$disgust_Turtle, na.rm = T),mean(dis$disgust_Rabbit, na.rm = T)), pch = 19, cex = 1.4)
# export 3.5 x 7 cm

# speed
boxplot(dis$speed_Crocodile, dis$speed_FinalWolf, dis$speed_FinalSnake, dis$speed_Scorpio, dis$speed_Deer, dis$speed_Pig,  dis$speed_Turtle, dis$speed_Rabbit, col = c(cR, cR, cR, cR, cB, cB, cB,cB), names = c("Crocodile", "Wolf", "Snake", "Scorpio", "Deer", "Pig", "Turtle", "Rabbit"), frame = FALSE, notch = F, ylab = "Ratings of speed", cex.lab = 1.2, cex.axis = 1, ylim = c(1,7))
abline(h=0, col="gray20", lwd = 1.3, lty = 2)

points(c(mean(dis$speed_Crocodile, na.rm = T), mean(dis$speed_FinalWolf, na.rm = T), mean(dis$speed_FinalSnake, na.rm = T), mean(dis$speed_Scorpio, na.rm = T), mean(dis$speed_Deer, na.rm = T),mean(dis$speed_Pig, na.rm = T),mean(dis$speed_Turtle, na.rm = T),mean(dis$speed_Rabbit, na.rm = T)), pch = 19, cex = 1.4)
# export 3.5 x 7 cm


### 4.3.  Block-by-block/mid-experimental threat ratings

# threatening vs non-threatening difference
mid_averaged <- d_sub_mid %>% 
  dplyr::group_by(ID, fear_object) %>%
  dplyr::summarize(threat = mean(threat, na.rm = T))

mid_averaged <- pivot_wider(mid_averaged, names_from = fear_object, values_from = threat)

shapiro.test(mid_averaged$False)
shapiro.test(mid_averaged$True)

wilcox.test(mid_averaged$True, mid_averaged$False, paired = T,  alternative = "two.sided", exact = F)
describe(mid_averaged$False)
describe(mid_averaged$True)

# block-by-block changes 
qb <- d_sub_mid %>% 
  dplyr::group_by(ID, fear_object, Round) %>%
  dplyr::summarize(threat = mean(threat, na.rm = T))
qb <- qb[qb$fear_object == "True",]

cR <- rgb(178/255, 31/255, 0/255)

boxplot(qb$threat[qb$Round == 1], qb$threat[qb$Round == 2], qb$threat[qb$Round == 3], qb$threat[qb$Round == 4],qb$threat[qb$Round == 5],qb$threat[qb$Round == 6], ylab = "Subjective threat", xlab = "Consecutive blocks", col = cR, 
frame = FALSE, notch = F, cex.lab = 1.2, cex.axis = 1)

points(c(mean(qb$threat[qb$Round == 1], na.rm = T), mean(qb$threat[qb$Round == 2], na.rm = T), mean(qb$threat[qb$Round == 3], na.rm = T), mean(qb$threat[qb$Round == 4], na.rm = T),mean(qb$threat[qb$Round == 5], na.rm = T),mean(qb$threat[qb$Round == 6], na.rm = T)), pch = 19, cex = 1.4)

# run analysis
fit_all <- aov_ez(data = qb, dv = "threat", id = "ID", within="Round", return = afex_options("return_aov"), anova_table = list(), fun_aggregate = mean)
fit_all 
summary(fit_all) # see epsilon values

# post-hoc comparisons (Bonferroni correction)
ref <- emmeans::emmeans(fit_all, specs = "Round")
ref
emmeans::contrast(ref,method="pairwise",adjust="bonferroni")

# Compare threat vs non-threat ratings before final block
d_sub_mid %>% 
  filter(Round == 6) %>% 
  group_by(ID, fear_object) %>% 
  dplyr::summarise(m_rat = mean(threat, na.rm=TRUE)) -> dat_r6

t.test(m_rat~fear_object, data = dat_r6, paired = TRUE)
shapiro.test(dat_r6 %>% 
               ungroup() %>% 
               filter(fear_object == "True") %>% 
               pull(m_rat))
shapiro.test(dat_r6 %>% 
               ungroup() %>% 
               filter(fear_object == "False") %>% 
               pull(m_rat))
wilcox.test(m_rat~fear_object, data = dat_r6, paired = TRUE)
# same result as t test



dat_r6 %>% 
  group_by(fear_object) %>% 
  dplyr::summarise(grand_m = mean(m_rat),
                   sd = sd(m_rat)) -> dat_r6_desc

dat_r6_desc

### 4.4. Stimulus recognition task
dm <- d_sub_mid
# % of unrecognized objects
length(dm$recognize[dm$recognize == 0]) / nrow(dm)
# from 18 subjects
length(unique(dm$ID[dm$recognize == 0]))

```

<a name="S5"></a>
&nbsp;

**5. Distance error as a function of subjective threat** 

```{r, warning=FALSE}

# merge initial and mid-experimental threat ratings to get overall average
dm <- d_sub_mid
dm <- dm %>% 
  group_by(ID, Stimulus) %>%
  dplyr::summarize(threat = mean(threat, na.rm = T))

di <- d_sub_start
di <- di %>% dplyr::rename("threat_start" = "threat")

d <- inner_join(dm, di)

# check correlations between initial and mid-experimental ratings
for (s in unique(d$Stimulus[d$fear_object == T])) {
  
ds <- d[d$Stimulus == s,]  

cor <- cor.test(ds$threat, ds$threat_start, method = "spearman") 
rho <- round(cor$estimate, digits = 3)
p_val <- round(cor$p.value, digits = 3)

scatter.smooth(ds$threat, ds$threat_start, main = paste0(s, "\n(rho = ", rho, ", p = ",p_val,")"), pch = 20, cex = 2, col = scales::alpha("firebrick",0.5), lwd = 2, xlim = c(0,7), ylim = c(0,7))
}

# merge data
dm <- d_sub_mid[,c(1,3,4,5,7)]
di <- d_sub_start
di <- di[,c(1,3,7,8)]
di$Round <- 0 # save initial rating as 'block 0'
dss <- rbind(di,dm)
dss <- dss[dss$fear_object == "True",]

# save average threat ratings
d <- dss %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(threat = mean(threat, na.rm = T))

# merge threat ratings with behavioral data
data_t <- data[data$FearObject == "True",]
dt <- merge(data_t,d, by = c("ID", "Stimulus"))

# prepare data for analysis & plotting
dt <- dt %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(distance_error  = mean(DistanceError), threat = mean(threat))

# plot raw figures with correlation results
for (s in unique(dt$Stimulus)) {

  ds <- dt[dt$Stimulus == s,]  

print(shapiro.test(ds$threat))
print(shapiro.test(ds$distance_error))

print(s)
cor <- cor.test(ds$threat, ds$distance_error, method = "spearman")
print(cor)

rho <- round(cor$estimate, digits = 3)
p_val <- round(cor$p.value, digits = 3)

scatter.smooth(ds$threat, ds$distance_error, main = paste0(s, "\n(rho = ", rho, ", p = ",p_val,")"), pch = 20, cex = 2, col = scales::alpha("firebrick",0.5), lwd = 2, xlim = c(1,7), ylim = c(-105,105))
}

# plot finalized figures
bold.text <- element_text(face = "bold", color = "black")
cR <- darken(rgb(178/255, 31/255, 0/255), 0.1)

par(mfrow=c(1,4))

for (s in unique(dt$Stimulus)) {

  d <- dt[dt$Stimulus == s,]  

Fig1 <- ggplot(data = d, aes(x = threat, y = distance_error)) + geom_smooth(col = cR, fill = cR,method = "lm", level=0.95, alpha = 0.5) +  geom_point(col = cR, alpha = 0.8, size = 3, shape = 19) +   labs(x = "Subjective Threat", y = "Distance Error") + scale_fill_manual() + theme_classic() +  theme(axis.text=element_text(size=16, colour = "black", face="bold"),  axis.title=element_text(size=18), axis.title.y = element_text(margin = margin(t = 0, r = 1, b = 0, l = 0)), axis.title.x =   element_text(margin = margin(t = 7, r = 0, b = 0, l = 0))) + theme(axis.title = bold.text) + xlim(1, 7) + ylim(-101, 101) + scale_x_continuous(n.breaks = 7)
print(Fig1) 
# export 4 x 4.5
}

```


<a name="S6"></a>
&nbsp;

**6. Distance error as a function anxiety levels, digust, and speed ratings** 

```{r, warning=FALSE}

### 6.1. Anxiety levels (STAI)

# prepare data
d <- data %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(distance_error = mean(DistanceError))
d <- merge(d, d_qstn, by = "ID")

# normality of distributions
shapiro.test(d$distance_error)
shapiro.test(d$stai_s)
shapiro.test(d$stai_t)

# test correlation: anxiety state - distance error
cor.test(d$stai_s, d$distance_error, method = "pearson")
bold.text <- element_text(face = "bold", color = "black")
Fig1 <- ggplot(data = d, aes(x = stai_s, y = distance_error)) + geom_smooth(col = "grey8", method = "lm", level=0.95, alpha = 0.5) +  geom_point(col = "grey 15", alpha = 0.5, size = 3, shape = 19) +   labs(x = "Anxiety - state", y = "Distance Error") + scale_fill_manual() + theme_classic() +  theme(axis.text=element_text(size=15, colour = "black", face="bold"),  axis.title=element_text(size=17), axis.title.y = element_text(margin = margin(t = 0, r = 3, b = 0, l = 0)), axis.title.x =   element_text(margin = margin(t = 5, r = 0, b = 0, l = 0))) + theme(axis.title = bold.text)
Fig1

# test correlation: anxiety trait - distance error
cor.test(d$stai_t, d$distance_error, method = "pearson")
bold.text <- element_text(face = "bold", color = "black")
Fig2 <- ggplot(data = d, aes(x = stai_t, y = distance_error)) + geom_smooth(col = "grey8", method = "lm", level=0.95, alpha = 0.5) +  geom_point(col = "grey 15", alpha = 0.5, size = 3, shape = 19) +   labs(x = "Anxiety - trait", y = "Distance Error") + scale_fill_manual() + theme_classic() +  theme(axis.text=element_text(size=15, colour = "black", face="bold"),  axis.title=element_text(size=17), axis.title.y = element_text(margin = margin(t = 0, r = 3, b = 0, l = 0)), axis.title.x =   element_text(margin = margin(t = 5, r = 0, b = 0, l = 0))) + theme(axis.title = bold.text)
Fig2

## check correlations for individual animals
# prepare data
d <- data %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(distance_error = mean(DistanceError))
d <- merge(d, d_qstn, by = "ID")

# loop over animals
for (s in unique(d$Stimulus)) {
ds <- d[d$Stimulus == s,]  
print(s)
print(shapiro.test(ds$distance_error))
cor <- cor.test(ds$stai_t, ds$distance_error, method = "spearman", exact = F)
print(cor)
rho <- round(cor$estimate, digits = 3)
p_val <- round(cor$p.value, digits = 3)
scatter.smooth(ds$stai_t, ds$distance_error, main = paste0(s, "\n(rho = ", rho, ", p = ",p_val,")"), pch = 20, cex = 2, col = scales::alpha("gray30",0.5), lwd = 2, xlim = c(25,55), ylim = c(-105,105))}

### 6.2. Disgust
dg <- d_sub_start
dg <- dg %>% 
  group_by(ID, Stimulus) %>%
  dplyr::summarize(disgust = mean(disgust, na.rm = T))

ds <- data %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(distance_error = mean(DistanceError))
ds <- merge(ds, dg, by = c("ID","Stimulus"))

# loop over animals
for (s in unique(ds$Stimulus)) {

print(s)
d <- ds[ds$Stimulus == s,]

test <- shapiro.test(d$distance_error)
norm1 <- (test$p.value > 0.05)
test <- shapiro.test(d$disgust)
norm2 <- (test$p.value > 0.05)

ifelse((norm1 == FALSE | norm2 == FALSE), R_method <- "spearman", R_method <- "pearson")  

print(s)
cor <- cor.test(d$disgust, d$distance_error, method = R_method)
print(cor)
rho <- round(cor$estimate, digits = 3)
p_val <- round(cor$p.value, digits = 3)

scatter.smooth(d$disgust, d$distance_error, main = paste0(s, " ", R_method, ":", rho, ", p = ",p_val), pch = 20, cex = 2, col = scales::alpha("chocolate4",0.5), lwd = 2, xlim = c(0,7), ylim = c(-105,105))
}

### 6.3. Speed
dsp <- d_sub_start
dsp <- dsp %>% 
  group_by(ID, Stimulus) %>%
  dplyr::summarize(speed = mean(how_fast, na.rm = T))

ds <- data %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(distance_error = mean(DistanceError))
ds <- merge(ds, dsp, by = c("ID","Stimulus"))

# loop over animals
for (s in unique(ds$Stimulus)) {

d <- ds[ds$Stimulus == s,]

test <- shapiro.test(d$distance_error)
norm1 <- (test$p.value > 0.05)
test <- shapiro.test(d$speed)
norm2 <- (test$p.value > 0.05)

ifelse((norm1 == FALSE | norm2 == FALSE), R_method <- "spearman", R_method <- "pearson")

print(s)
cor <- cor.test(d$speed, d$distance_error, method = R_method)
print(cor)
rho <- round(cor$estimate, digits = 3)
p_val <- round(cor$p.value, digits = 3)

scatter.smooth(d$speed, d$distance_error, main = paste0(s, " ", R_method, ":", rho, ", p = ",p_val), pch = 20, cex = 2, col = scales::alpha("darkblue",0.5), lwd = 2, xlim = c(0,7), ylim = c(-105,105))
}

```


<a name="S7"></a>
&nbsp;

**7. Cybersickness (SSQ) and presence in VR (SUS)** 

```{r}

### 7.1. Simulator Sickness Questionnaire (SSQ)
d_qstn$SSQ.Pre <- d_qstn$SSQ.Pre / 6
d_qstn$SSQ.Post <- d_qstn$SSQ.Post / 6
d_qstn$csickness_change <- d_qstn$SSQ.Post - d_qstn$SSQ.Pre
hist(d_qstn$csickness_change, col = "darkgreen")

shapiro.test(d_qstn$SSQ.Pre)
shapiro.test(d_qstn$SSQ.Post)
wilcox.test(d_qstn$SSQ.Post, d_qstn$SSQ.Pre, paired = T, exact = F)

describe(d_qstn$SSQ.Pre)
describe(d_qstn$SSQ.Post)


### 7.2 Slater-Usoh-Steed Questionnaire (SUS; Slater, 1999) 
d_qstn$SUS <- d_qstn$SUS / 6
describe(d_qstn$SUS)
dt <- data %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(distance_error  = mean(DistanceError), localization_error =  mean(LocalizationError))
dt <- merge(dt, d_qstn, by = "ID")

shapiro.test(dt$SUS.Score)
shapiro.test(dt$distance_error)
shapiro.test(dt$localization_error)

#scatter.smooth(dt$SUS.Score, dt$distance_error)
cor.test(dt$SUS.Score, dt$distance_error, method = "pearson")

#scatter.smooth(dt$SUS.Score, dt$localization_error)
cor.test(dt$SUS.Score, dt$localization_error, method = "spearman")

```

<a name="S8"></a>
&nbsp;

**8. Distance errors as function of real distance** 
```{r}

### Plot distance errors as function of real distance for different animals
 
for (p in unique(data$Stimulus)) {

subdata <- data[data$Stimulus == p,]

Figure <- ggplot(data = subdata, aes(x = RealDistance, y = DistanceError)) +
  geom_point(col = "grey 15", alpha = 0.2, size = 1, shape = 18) +
  geom_smooth(col = "grey8", method = "loess", level=0.95, alpha = 0.9) +
  labs(y = "Distance Error", x = "True Distance") +
  ggtitle(p) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 17), axis.text=element_text(size=15),  axis.title=element_text(size=15)) +
  scale_x_continuous(limits= c(min(data$RealDistance), max(data$RealDistance)), expand = c(0.01,0.01)) +
  scale_y_continuous(limits= c(-250, 250), expand = c(0.01,0.01)) + geom_hline(yintercept = 0, col = "royalblue1")
plot(Figure)

}
```


<a name="S9"></a>
&nbsp;

**9. Distribution of stimulus onsets across the cardiac cycle** 
```{r}

# specify a data frame with the uniformity test results for each participant
Onset_distribution_ID <- data.frame(ID = integer(0),
                                    T_test_statistics = numeric(0), # T - threatening
                                    T_p_value = numeric(0), # T - threatening
                                    NT_test_statistics = numeric(0), # NT - non-threatening
                                    NT_p_value = numeric(0)) #NT - non-threatening

for (p in unique(data$ID)) { # LOOP PARTICIPANTS (p)
  
  # save the vector with calculated onset positions in radians as a circular object
  T_temp_onset <- circular(data$relPosRRrad[data$ID==p & data$FearObject == "True"], type="angles", units="radians", rotation="clock") 
  
  NT_temp_onset <- circular(data$relPosRRrad[data$ID==p & data$FearObject == "False"], type="angles", units="radians", rotation="clock")

  # test uniformity of onset distribution for a participant and save the results
  T_onset_distribution_individual <- rayleigh.test(T_temp_onset) 
  NT_onset_distribution_individual <- rayleigh.test(NT_temp_onset) 
  
  # add test statistics and p-value to the data frame with uniformity testing results
  T_p_value <- T_onset_distribution_individual$p.value
  T_test_statistics <- T_onset_distribution_individual$statistic
  NT_p_value <- NT_onset_distribution_individual$p.value
  NT_test_statistics <- NT_onset_distribution_individual$statistic
  
  Onset_distribution_ID[nrow(Onset_distribution_ID)+1,] <- c(p, T_test_statistics, T_p_value, NT_test_statistics, NT_p_value)
}

## Optional histograms
hist(as.numeric(Onset_distribution_ID$T_test_statistics), breaks = 20)
hist(as.numeric(Onset_distribution_ID$T_p_value), breaks = 20)
hist(as.numeric(Onset_distribution_ID$NT_test_statistics), breaks = 20)
hist(as.numeric(Onset_distribution_ID$NT_p_value), breaks = 20)


```
