---
title: <font size="5">**VRCC -- main analysis **</font>
author: <br> <font size="4"> Pawel Motyka, Felix Klotzsche, Aleksander Molak </font>
  <br>  pmotyka@psych.pan.pl <br>klotzsche@cbs.mpg.de <br>aleksander.molak@gmail.com
date: <font size="3"> Jan 2024  </font>
output:
  html_document: default
  pdf_document: default
chunk_output_type: console
self_contained: no
--- 

&nbsp;
<font size="4">
**List of sections**:  

- [S1](#S1) – Load required packages and data
- [S2](#S2) – Data checks and descriptive statistics of dep. variables 
- [S3](#S3) – Hypothesis 1: Comparison of distance error between threatening and non-threatening objects 
- [S4](#S4) – Hypothesis 2: Comparison of distance error between cardiac phases 
- [S5](#S5) – Comparison of distance error between cardiac phases (individual animals) 
- [S6](#S6) – Distance errors as a function of true distance (individual animals) 
- [S7](#S7) – Width of distance error distributions as function of threat and cardiac phase 


<a name="S1"></a>
&nbsp;

**1. Load required packages and data** 

```{r message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# define colors:
c_threat <- "#FE5D9F"
c_nonthreat <- "#54426B"
c_neutral <- "#623CEA"
c_systole <- "#F686BD"
c_diastole <- "#F4BBD3"
basic_color <- '#195e8c'


# Utils
library(tidyverse)
library(dplyr) 
library(here)
library(tidyr)


# load helper functions
source(here::here("./Code/Analyses/VRTask/Utils/stats_utils.r"))

# Plotting and tables
library(ggplot2)
library(sjPlot)
library(gghalves)
library(ggridges)
library(scales)
library(colorspace)
library(Rmisc)

# Statistical tools
library(lme4)
library(lmtest)
library(lmerTest)
library(car)
library(effsize)
library(psych)
library(equivalence)
library(BayesFactor)
library(circular) 
library(afex)

# Set up the fulldata directory
VRCC_dir         <- here::here()

# Read the preprocessed data
data <- read.csv(file = paste0(VRCC_dir,"/Data/VRTask/VRCC_data_consolidated-2023-08-10.csv"))

# conversion of distance from m to cm
data <- data %>%
  mutate(EstimatedDistance = EstimatedDistance * 100,
         RealDistance = RealDistance * 100,
         DistanceError = DistanceError * 100,
         DistanceErrorAbs = DistanceErrorAbs * 100,
         LocalizationError = LocalizationError * 100)


```

<a name="S2"></a>
&nbsp;

**2. Data checks and descriptive statistics** 

```{r, warning=FALSE}

# --- Control analysis: avg. distance and angular errors different from zero? ---

# Transform angular error from radians to degree:
data$AngularErrorDeg <- data$AngularErrorRad * 180 / pi 
data$AngularErrorDegAbs <- abs(data$AngularErrorDeg)

dd <- data %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(mean_distance = mean(DistanceError),
                   mean_angular = mean(AngularErrorDeg))

# check whether average distance error was different from zero
shapiro.test(dd$mean_distance)
t.test(dd$mean_distance, mu = 0, alternative = "two.sided")
describe(dd$mean_distance)

# check whether average angular error was different from zero
shapiro.test(dd$mean_angular)
wilcox.test(dd$mean_angular, mu = 0, alternative = "two.sided")
t.test(dd$mean_angular, mu = 0, alternative = "two.sided")
describe(dd$mean_angular)
hist(dd$mean_angular)
# wilcox & t test largely agree (not surprising due to reasonable sample size; for sake of simplicity we can therefore just report the t test)


# calculate the ratio of systolic and diastolic trials:
n_per_c_phase <- data %>%
  mutate(systolength = systolength - 50) %>%   # subtract buffer after R-peak
  group_by(c_phase, ID) %>% 
  dplyr::summarize(n = n(), .groups = "drop_last") %>% 
  dplyr::summarize(n = mean(n)) %>% 
  ungroup()

n_sys_trials <- n_per_c_phase$n[n_per_c_phase$c_phase == "systole"]
n_dia_trials <- n_per_c_phase$n[n_per_c_phase$c_phase == "diastole"]

cat("################ \nNumber of trials per cardiac phase:\n")
cat(sprintf("(Avg.) number of systolic trials: %f \n(Avg.) number of diastolic trials: %f \nRatio: %f \n\n", n_sys_trials, n_dia_trials, n_sys_trials / n_dia_trials))

dur_per_c_phase <- data %>% 
  mutate(systolength = systolength - 50) %>%   # subtract buffer after R-peak
  group_by(ID) %>% 
  dplyr::summarize(m_sys = mean(systolength),
                   m_dia = mean(RRLength - systolength - 150), 
                   .groups = "drop_last") %>% 
  dplyr::summarise(m_sys = mean(m_sys),
                   m_dia = mean(m_dia), 
                   .groups = NA) %>% 
  ungroup()

dur_sys <- dur_per_c_phase$m_sys[1]
dur_dia <- dur_per_c_phase$m_dia[1]

cat(sprintf("(Avg.) duration of systolic window: %f \n(Avg.) duration of diastolic window: %f \nRatio: %f", dur_sys, dur_dia, dur_sys / dur_dia))

```


<a name="S3"></a>
&nbsp;

**3. Hypothesis 1: Comparison of distance error between threatening and non-threatening objects** 

```{r warning=FALSE}

# 3.1. Preregistered analysis: compare distance error between threat and non-threat

d <- data %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(mean_threat = mean(DistanceError[FearObject == "True"]), 
                   mean_nonthreat = mean(DistanceError[FearObject == "False"]),
                   sd_threat = sd(DistanceError[FearObject == "True"]), 
                   sd_nonthreat = sd(DistanceError[FearObject == "False"]))

# check normality of distributions
shapiro.test(d$mean_threat)
shapiro.test(d$mean_nonthreat)

# perform paired t-test
t.test(d$mean_threat, d$mean_nonthreat, alt = "two.sided", conf = 0.95, paired = T) 

# calculate Cohen's d
effsize::cohen.d(d$mean_threat, d$mean_nonthreat, paired = T)

# show summary statistics
describe(d$mean_threat)
describe(d$mean_nonthreat)

## Compare the precision (SD) between threatening and non-threatening animals
# check normality of distributions
shapiro.test(d$sd_threat)
shapiro.test(d$sd_nonthreat)

# perform paired t-test
t.test(d$sd_threat, d$sd_nonthreat, alt = "two.sided", conf = 0.95, paired = T) 

# calculate Cohen's d
effsize::cohen.d(d$sd_threat, d$sd_nonthreat, paired = T)

# show summary statistics
describe(d$sd_threat)
describe(d$sd_nonthreat)


# for how many subjects threatening animals were perceived as closer than non-threatening ones
d$diff_distances <- d$mean_nonthreat - d$mean_threat
length(d$diff_distances[d$diff_distances > 0])
hist(d$diff_distances)


```



```{r}
# 3.2. Plot results - hypothesis 1

# specify colors
cR <- rgb(178/255, 31/255, 0/255)    # altern.: c_threat         # Old value: rgb(178/255, 31/255, 0/255)
cB <- rgb(10/255, 80/255, 200/255)   # altern.: c_nonthreat      # Old value:  rgb(10/255, 80/255, 200/255)

# prepare data

d <- data %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(mean_threat = mean(DistanceError[FearObject == "True"]), 
                   mean_non_threat = mean(DistanceError[FearObject == "False"]))
d <- gather(d, threat, distance_error, mean_threat:mean_non_threat)
d$threat_f[d$threat == "mean_threat"] <- 1
d$threat_f[d$threat == "mean_non_threat"] <- 2
d$pos <- jitter(d$threat_f, amount=.03)
m_threat <- mean(d$distance_error[d$threat == "mean_threat"])
m_nonthreat <- mean(d$distance_error[d$threat == "mean_non_threat"])

# get standard deviations
score_sd_2 <- sd(d$distance_error[d$threat == "mean_non_threat"])
score_sd_1 <- sd(d$distance_error[d$threat == "mean_threat"])

# get standard errors
score_se_2 <- score_sd_2/sqrt(length(unique(d$ID))) 
score_se_1 <- score_sd_1/sqrt(length(unique(d$ID)))

# get confidence intervals (95%)
score_ci_2 <- CI(d$distance_error[d$threat == "mean_non_threat"], ci = 0.95)
score_ci_1 <- CI(d$distance_error[d$threat == "mean_threat"], ci = 0.95)
ci <- c((score_ci_1[1] - score_ci_1[3]), (score_ci_2[1] - score_ci_2[3]))

# create ggplot
f1 <- ggplot(data = d, aes(y = distance_error)) +
  
  #Add geom_() objects
  geom_point(data = d %>% filter(threat_f =="1"),
             aes(x = pos),
             color = cR,
             size = 1.5,
             alpha = .4) +

  geom_point(data = d %>% filter(threat_f =="2"),
             aes(x = pos),
             color = cB,
             size = 1.5,
             alpha = .4) + 
  
  geom_line(aes(x = pos, group = ID),
            color = 'gray60',
            alpha = .3) +
  
  geom_half_boxplot(
    data = d %>% filter(threat_f=="1"), 
    aes(x=threat_f, y = distance_error), 
    position = position_nudge(x = -.25), 
    side = "r",
    outlier.shape = NA, 
    center = TRUE, 
    errorbar.draw = FALSE, 
    width = .2, 
    fill = cR) +
  
  geom_half_boxplot(
    data = d %>% filter(threat_f=="2"), 
    aes(x=threat_f, y = distance_error), 
    position = position_nudge(x = .15), 
    side = "r",
    outlier.shape = NA, 
    center = TRUE, 
    errorbar.draw = FALSE, 
    width = .2, 
    fill = cB) +
  
  geom_half_violin(
    data = d %>% filter(threat_f=="1"),
    aes(x = threat_f, y = distance_error), 
    position = position_nudge(x = -.3), 
    side = "l", fill = cR) +
  
  geom_half_violin(
    data = d %>% filter(threat_f=="2"),
    aes(x = threat_f, y = distance_error), 
    position = position_nudge(x= .3), 
    side = "r", 
    fill = cB) +
  
  geom_point(data = d %>% filter(threat_f=="1") %>% 
                          filter(row_number() == 1),
            aes(x = threat_f, y = m_threat), 
            position = position_nudge(x = .0), 
            color = darken(cR,0.3), 
            size = 5.5, 
            shape = 20) +
  
  geom_point(data = d %>% filter(threat_f=="2") %>% 
                          filter(row_number() == 1),
            aes(x = threat_f, y = m_nonthreat),
            position = position_nudge(x = -.0),
            color = darken(cB, 0.3),
            size = 5.5,
            shape = 20) + 
  geom_line(data = tibble(x = c(1,2),
                         y = c(m_threat, m_nonthreat)),
           aes(x = x, y = y)) +
  
  scale_x_continuous(breaks=c(1,2),
                     labels=c("Threatening", "Non-threatening")) +
  xlab("Type of animal") + 
  ylab("Distance Error (cm)") +
  ggtitle('Threatening vs Non-threatening animals') +
  theme_classic()+
  coord_cartesian(ylim=c(min(d$distance_error), 90)) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.title = element_text(face="bold",
                                  size=18.5,
                                  colour = "black"),
        axis.text = element_text(face="bold",
                                 size=17,
                                 colour = "black"))

f1 

# save to disc:
fpath_figs <- file.path(VRCC_dir, 'Code', 'Analyses', 'VRTask', 'Figures')
fname <- file.path(fpath_figs, 'VRCC_DistErr_BoxViolin.pdf')
pdf(fname)
f1
dev.off()


# Plot results for single animals

# Overview box plot:
d <- data %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(distance_error = mean(DistanceError))

d <- spread(d, key = Stimulus, value = distance_error)

boxplot(d$Crocodile, d$FinalWolf, d$FinalSnake, d$Scorpio, d$Deer, d$Pig,  d$Turtle, d$Rabbit, 
        col = c(cR, cR, cR, cR, cB, cB, cB,cB), 
        names = c("Crocodile", "Wolf", "Snake", "Scorpio", "Deer", "Pig", "Turtle", "Rabbit"),
        frame = FALSE,
        notch = TRUE,
        ylab = "Distance Error", 
        cex.lab = 1.4, 
        cex.axis = 1)
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


# pub-ready density plot:
data_avg <- data %>%
  group_by(Stimulus, ID) %>%
  dplyr::summarize(DistanceError = mean(DistanceError), 
                   FearObject = first(FearObject)) %>%
  mutate(Stimulus = revalue(Stimulus, c('FinalWolf'='Wolf', 
                                        'FinalSnake' = 'Snake',
                                        'Scorpio' = 'Scorpion'))) %>% 
  ungroup()



ggplot(data_avg, aes(x = DistanceError, 
                     y = fct_reorder(Stimulus, .x = DistanceError, .fun=mean),
                     fill = FearObject)) +
  geom_density_ridges(aes(point_fill = factor(FearObject),
                          point_color= factor(FearObject)),
                      alpha = 0.9,
                      jittered_points = TRUE, 
                      point_alpha=1,
                      point_shape=21, 
                      stat = "density_ridges") +
  theme_ridges() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_text(hjust = 0.5),  # Center x-axis label
        axis.title.y = element_text(hjust = 0.5)) +
  geom_vline(xintercept = 0, color = c_neutral) + 
  scale_fill_manual(values = c(c_nonthreat, c_threat)) + 
  scale_discrete_manual(aesthetics = "point_color", values = c("black", "black")) +
  scale_discrete_manual(aesthetics = "point_fill", values = c(c_threat, c_nonthreat)) +
  ylab("Stimulus animal") +
  xlab("Distance error (°)") +
  coord_flip() -> plt

plt

# save to disc:
fpath_figs <- file.path(VRCC_dir, 'Code', 'Analyses', 'VRTask', 'Figures')
fname <- file.path(fpath_figs, 'VRCC_DistErr_RidgeDensity.pdf')
pdf(fname)
plt
dev.off()



```

**Exploratory/control analysis: compare angular error between threat and non-threat**
<a name="S3c"></a>
&nbsp;

```{r warning=FALSE}

# 3.3 Exploratory/control analysis: compare angular error between threat and non-threat
d <- data %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(mean_threat = mean(AngularErrorDeg[FearObject == "True"]), 
                   mean_non_threat = mean(AngularErrorDeg[FearObject == "False"]))

# check normality of distributions
shapiro.test(d$mean_threat)
shapiro.test(d$mean_non_threat)

# perform paired t-test
t.test(d$mean_threat, d$mean_non_threat, alt = "two.sided", conf = 0.95, paired = T) 

# calculate Cohen's d
effsize::cohen.d(d$mean_threat, d$mean_non_threat, paired = T)

# show summary statistics
describe(d$mean_threat)
describe(d$mean_non_threat)

d <- data %>% 
  dplyr::group_by(ID, FearObject) %>%
  dplyr::summarize(mean_AngErr = mean(AngularErrorDeg),
                   mean_DistErr = mean(DistanceError),
                   sd_AngErr = sd(AngularErrorDeg),
                   sd_DistErr = sd(DistanceError),
      ) %>% 
  ungroup()

# check normality of distributions
shapiro.test(d$sd_AngErr[d$FearObject=="True"])
shapiro.test(d$sd_AngErr[d$FearObject=="False"])


t.test(d$sd_AngErr[d$FearObject=="True"], d$sd_AngErr[d$FearObject=="False"], paired = TRUE, alternative = "two.sided")


# Show means:
d %>% group_by(FearObject) %>% 
  dplyr::summarise(gmean_AngErrDeg = mean(mean_AngErr),
                   gmean_DistErr = mean(mean_DistErr),
                   meansd_AngErrDeg = mean(sd_AngErr),
                   meansd_DistErr = mean(sd_DistErr)
                   ) -> summary_AngDistErr

print(summary_AngDistErr)

###3.3 Plot results for different animals
d <- data %>% 
  dplyr::group_by(ID, Stimulus) %>%
  dplyr::summarize(angular_error = mean(AngularErrorDeg))

d <- spread(d, key = Stimulus, value = angular_error)

boxplot(d$Crocodile, d$FinalWolf, d$FinalSnake, d$Scorpio, d$Deer, d$Pig,  d$Turtle, d$Rabbit, 
        col = c(cR, cR, cR, cR, cB, cB, cB,cB), 
        names = c("Crocodile", "Wolf", "Snake", "Scorpio", "Deer", "Pig", "Turtle", "Rabbit"), 
        frame = FALSE, 
        notch = TRUE, 
        ylab = "Angular Error", 
        cex.lab = 1.4, 
        cex.axis = 1)
abline(h=0, col="gray20", lwd = 1.3, lty = 2)
```



<a name="S4"></a>
&nbsp;

**4. Hypothesis 2: Comparison of distance error between cardiac phases** 

*Binary comparison: ANOVA*

```{r}

# 4.1. 2 x 2 ANOVA analysis (with Bonferroni post hoc comparisons)

# prepare data
d <- data[data$c_phase == "systole" | data$c_phase == "diastole",]
d <- dplyr::select(d, ID, DistanceError, c_phase, FearObject)
d <- d %>% 
  dplyr::group_by(ID, c_phase, FearObject) %>% 
  dplyr::summarize(DistanceError = mean(DistanceError))

# run analysis
fit_all <- aov_ez(data = d,
                  dv = "DistanceError",
                  id = "ID",
                  within=c("c_phase", "FearObject"),
                  return = afex_options("return_aov"),
                  anova_table = list(),
                  fun_aggregate = mean)
fit_all 
summary(fit_all) # see epsilon values

# post-hoc comparisons (Bonferroni correction)
ref <- emmeans::emmeans(fit_all, specs = c("c_phase", "FearObject"))
ref
emmeans::contrast(ref,method="pairwise",adjust="bonferroni")


```


*Binary comparison: Mixed Model (pre-registered)*

```{r warning=FALSE}
### 4.2. Preregistered mixed model

d <- data[data$c_phase == "systole" | data$c_phase == "diastole",]
d <- d %>% 
  mutate(RealDistance = RealDistance * 0.01,
         DistanceError = DistanceError * 0.01)

# null model
null_model <- lmer(DistanceError ~ 1 + (1 + RealDistance | ID), data = d)
summary(null_model)
# warnings to be ignored (absent when rescaling distance errors to metres)

# full model
full_model <- lmer(DistanceError ~ c_phase * FearObject + (1 + RealDistance|ID), data = d)
summary(full_model)
get_r2_mlm(full_model) # alternative: performance::r2

# plot model
plot_model(full_model, type = "int", mdrt.values = "meansd", colors = c(c_nonthreat, c_threat))

# compare models
lrtest(null_model, full_model)
```

*Bayes factors*

```{r}
# 4.3. Bayes factor analysis (comparisons of interest)

## Threatening animals
d <- data[data$FearObject == "True",]
d <- d[d$c_phase == "systole" | d$c_phase == "diastole", ]

# transform data
d <- d %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(m_systole  = mean(DistanceError[c_phase == "systole"]), 
            m_diastole = mean(DistanceError[c_phase == "diastole"]))

# t-test (comparison of interest)
shapiro.test(d$m_systole)
shapiro.test(d$m_diastole)
t.test(d$m_systole, d$m_diastole, paired = T)


# Bayes factor (comparison of interest + robustness check)
ttestBF(d$m_systole, d$m_diastole, paired = T)
ttestBF(d$m_systole, d$m_diastole, paired = T, r = 1)
ttestBF(d$m_systole, d$m_diastole, paired = T, r = 0.354)

## Non-threatening animals
d <- data[data$FearObject == "False",]
d <- d[d$c_phase == "systole" | d$c_phase == "diastole", ]

# transform data
d <- d %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(
    m_systole = mean(DistanceError[c_phase == "systole"]), 
    m_diastole = mean(DistanceError[c_phase == "diastole"])
  )

# t-test (comparison of interest)
shapiro.test(d$m_systole)
shapiro.test(d$m_diastole)
t.test(d$m_systole, d$m_diastole, paired = T)

# Bayes factor (comparison of interest + robustness check)
ttestBF(d$m_systole, d$m_diastole, paired = T)
ttestBF(d$m_systole, d$m_diastole, paired = T, r = 1)
ttestBF(d$m_systole, d$m_diastole, paired = T, r = 0.354)
```

*Binary analysis: Plots*
```{r}

# 4.4. Vizualize the results

# Threatening
d <- data[data$FearObject == "True",]
d <- d[d$c_phase == "systole" | d$c_phase == "diastole", ]

# transform data
d <- d %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(
    m_systole = mean(DistanceError[c_phase == "systole"]), 
    m_diastole = mean(DistanceError[c_phase == "diastole"]),
    m_systole_ang = mean(AngularErrorDeg[c_phase == "systole"]), 
    m_diastole_ang = mean(AngularErrorDeg[c_phase == "diastole"])
  )

# t-test (comparison of interest)
shapiro.test(d$m_systole)
shapiro.test(d$m_diastole)
shapiro.test(d$m_systole_ang)
shapiro.test(d$m_diastole_ang)
t.test(d$m_systole, d$m_diastole, paired = T)
t.test(d$m_systole_ang, d$m_diastole_ang, paired = TRUE)



d2 <- d
d2$diff <- d$m_diastole - d$m_systole
#hist(d2$diff, breaks = 20)
length(d2$diff[d2$diff < 0]) # closer at diastole


d <- gather(d, phase, distance_error, m_systole:m_diastole)
d$phase_f[d$phase == "m_systole"] <- 1
d$phase_f[d$phase == "m_diastole"] <- 2
d$pos <- jitter(d$phase_f, amount=.03)

# threatening
c_threat_sys <- lighten(c_threat, amount = 0.35)   #  "#6c030f"
c_threat_dias <- darken(c_threat, amount = 0.15)  # "#af7d81"

f1 <- ggplot(data = d, aes(y = distance_error)) +
  
  geom_point(data = d %>% filter(phase_f =="1"), aes(x = pos), color = c_threat_sys, size = 1.5, 
             alpha = .5) +
  geom_point(data = d %>% filter(phase_f =="2"), aes(x = pos), color = c_threat_dias, size = 1.5, 
             alpha = .5) +
  geom_line(aes(x = pos, group = ID), color = 'gray60', alpha = .3) +
  
  geom_half_boxplot(
    data = d %>% filter(phase_f=="1"), aes(x=phase_f, y = distance_error), position = position_nudge(x = -.25), 
    side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = FALSE, width = .2, 
    fill = c_threat_sys) +
  
  geom_half_boxplot(
    data = d %>% filter(phase_f=="2"), aes(x=phase_f, y = distance_error), position = position_nudge(x = .15), 
    side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = FALSE, width = .2, 
    fill = c_threat_dias) +
  
  geom_half_violin(
    data = d %>% filter(phase_f=="1"),aes(x = phase_f, y = distance_error), position = position_nudge(x = -.3), 
    side = "l", fill = c_threat_sys) +
  
  geom_half_violin(
    data = d %>% filter(phase_f=="2"),aes(x = phase_f, y = distance_error), position = position_nudge(x= .3), 
    side = "r", fill = c_threat_dias) +
    
  geom_point(data = d %>% 
              group_by(phase_f) %>% 
              dplyr::summarize(gm_DistErr = mean(distance_error)) %>% 
              mutate(col = factor(phase_f)), 
              #mutate(loc = if_else(c_phase == "systole", 1, 2)),
            aes(x = phase_f, y = gm_DistErr, color = col), 
            position = position_nudge(x = -.0),
            size = 5.5,
            shape = 20) +
  
  geom_line(data = d %>% 
              group_by(phase_f) %>% 
              dplyr::summarize(gm_DistErr = mean(distance_error)), 
              #mutate(loc = if_else(c_phase == "systole", 1, 2)),
            aes(x = phase_f, y = gm_DistErr)) +
  
  #Define additional settings
  scale_x_continuous(breaks=c(1,2), labels=c("Systole", "Diastole")) +
  scale_color_manual(values = c(c_threat_sys, c_threat_dias)) + 
  
  #Define additional settings
  scale_x_continuous(breaks=c(1,2), labels=c("Systole", "Diastole")) +
  xlab("Cardiac phase") + ylab("Distance Error") +
  ggtitle('Threatening animals') +
  theme_classic()+
  coord_cartesian(ylim=c(-100, 80)) +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.title = element_text(face="bold",size=18, colour = "black"), axis.text = element_text(face="bold",size=17, colour = "black"))
f1 # export size: 5 x 5

# save to disc:
fpath_figs <- file.path(VRCC_dir, 'Code', 'Analyses', 'VRTask', 'Figures')
fname <- file.path(fpath_figs, 'VRCC_DistErr_BoxViolin_CardiacPhase_Threat.pdf')
pdf(fname)
f1
dev.off()



### Non_threatening
c_nonthreat_sys <- lighten(c_nonthreat, amount = 0.35)   #  "#6c030f"   # darken(rgb(10/255, 80/255, 200/255),0.55)
c_nonthreat_dias <- darken(c_nonthreat, amount = 0.15)  # "#9590a8"

d <- data[data$FearObject == "False",]
d <- d[d$c_phase == "systole" | d$c_phase == "diastole", ]

d <- d %>% 
  dplyr::group_by(ID) %>%
  dplyr::summarize(m_systole = mean(DistanceError[c_phase == "systole"]), 
            m_diastole = mean(DistanceError[c_phase == "diastole"]))


d2 <- d
d2$diff <- d$m_diastole - d$m_systole
#hist(d2$diff, breaks = 20)
length(d2$diff[d2$diff < 0])

d <- gather(d, phase, distance_error, m_systole:m_diastole)
d$phase_f[d$phase == "m_systole"] <- 1
d$phase_f[d$phase == "m_diastole"] <- 2
d$pos <- jitter(d$phase_f, amount=.03)

f2 <- ggplot(data = d, aes(y = distance_error)) +
  
  #Add geom_() objects
  geom_point(data = d %>% filter(phase_f =="1"), aes(x = pos), color = c_nonthreat_sys, size = 1.5, 
             alpha = .5) +
  geom_point(data = d %>% filter(phase_f =="2"), aes(x = pos), color = c_nonthreat_dias, size = 1.5, 
             alpha = .5) +
  geom_line(aes(x = pos, group = ID), color = 'gray60', alpha = .3) +
  
  geom_half_boxplot(
    data = d %>% filter(phase_f=="1"), aes(x=phase_f, y = distance_error), position = position_nudge(x = -.25), 
    side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = FALSE, width = .2, 
    fill = c_nonthreat_sys) +
  
  geom_half_boxplot(
    data = d %>% filter(phase_f=="2"), aes(x=phase_f, y = distance_error), position = position_nudge(x = .15), 
    side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = FALSE, width = .2, 
    fill = c_nonthreat_dias) +
  
  geom_half_violin(
    data = d %>% filter(phase_f=="1"),aes(x = phase_f, y = distance_error), position = position_nudge(x = -.3), 
    side = "l", fill = c_nonthreat_sys) +
  
  geom_half_violin(
    data = d %>% filter(phase_f=="2"),aes(x = phase_f, y = distance_error), position = position_nudge(x= .3), 
    side = "r",fill = c_nonthreat_dias) +
  
  geom_point(data = d %>% 
              group_by(phase_f) %>% 
              dplyr::summarize(gm_DistErr = mean(distance_error)) %>% 
              mutate(col = factor(phase_f)), 
              #mutate(loc = if_else(c_phase == "systole", 1, 2)),
            aes(x = phase_f, y = gm_DistErr, color = col), 
            position = position_nudge(x = -.0),
            size = 5.5,
            shape = 20) +
  
  geom_line(data = d %>% 
              group_by(phase_f) %>% 
              dplyr::summarize(gm_DistErr = mean(distance_error)), 
              #mutate(loc = if_else(c_phase == "systole", 1, 2)),
            aes(x = phase_f, y = gm_DistErr)) +
  
  #Define additional settings
  scale_x_continuous(breaks=c(1,2), labels=c("Systole", "Diastole")) +
  scale_color_manual(values = c(c_nonthreat_sys, c_nonthreat_dias)) + 
  xlab("Cardiac phase") + ylab("Distance Error") +
  ggtitle('Non-threatening animals') +
  theme_classic()+
  coord_cartesian(ylim=c(-100, 80)) +
   theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"), 
         axis.title = element_text(face="bold",
                                   size=18, 
                                   colour = "black"), 
         axis.text = element_text(face="bold",size=17, colour = "black"))
f2 # export size: 5 x 5

# save to disc:
fpath_figs <- file.path(VRCC_dir, 'Code', 'Analyses', 'VRTask', 'Figures')
fname <- file.path(fpath_figs, 'VRCC_DistErr_BoxViolin_CardiacPhase_NonThreat.pdf')
pdf(fname)
f2
dev.off()

# ANOVA plot: 

d <- data %>% 
  filter(c_phase == "systole" | c_phase == "diastole") %>% 
  group_by(ID, c_phase, FearObject) %>% 
  dplyr::summarise(m_DistErr = mean(DistanceError)) %>% 
  mutate(c_phase = factor(c_phase, 
                          levels = c("systole", "diastole"), 
                          labels = c("Systole", "Diastole")),
         FearObject = factor(FearObject,
                             levels = c( "True" , "False"), 
                             labels = c("Threatening", "Non-threatening")),
         Color = if_else(FearObject == "Threatening", 
                         if_else(c_phase == "Systole", 
                                 c_threat_sys, 
                                 c_threat_dias),
                         if_else(c_phase == "Systole", 
                                 c_nonthreat_sys, 
                                 c_nonthreat_dias)))
                         
f3 <- ggplot(data = d, aes(x = c_phase, y = m_DistErr, fill = Color)) +
  geom_boxplot(aes(), 
               outlier.shape = NA, 
               center = TRUE, errorbar.draw = FALSE, width = .2) + 
  xlab("Cardiac phase") + ylab("Distance Error") +
  theme_classic()+
  scale_fill_manual(values = c(c_threat_sys, c_threat_dias, c_nonthreat_sys, c_nonthreat_dias),
                    name="") +
  coord_cartesian(ylim=c(-70, 70)) +
   theme(panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"), 
         axis.title = element_text(face="bold",size=18, colour = "black"), 
         axis.text = element_text(face="bold",size=17, colour = "black"))
f3

# save to disc:
fpath_figs <- file.path(VRCC_dir, 'Code', 'Analyses', 'VRTask', 'Figures')
fname <- file.path(fpath_figs, 'VRCC_DistErr_BoxPlot_ANOVA.pdf')
pdf(fname)
f3
dev.off()



```

**Circular analysis (pre-registered): Mixed Model**

```{r}
# 4.5 Run preregistered analysis (circular approach)

# get circular components
rel_pos_circular <- get_circular_components(data$relPosRRrad, 2 * pi)

# add them to data
data$relPosRRradCircCos <- rel_pos_circular$cos_component
data$relPosRRradCircSin <- rel_pos_circular$sin_component

d <- data %>% 
  mutate(RealDistance = RealDistance * 0.01,
         DistanceError = DistanceError * 0.01)

# null model
null_model <- lmer(DistanceError ~ 1 + (1 + RealDistance|ID), data = d, REML = FALSE)
summary(null_model)

# full model
full_model <- lmer(DistanceError ~ relPosRRradCircCos * FearObject + relPosRRradCircSin * FearObject + (1 + RealDistance|ID), data = d, REML = FALSE)
summary(full_model)
plot_model(full_model, type = "int", mdrt.values = "meansd")
get_r2_mlm(full_model)

# compare models
lrtest(null_model, full_model)
comparison <- anova(null_model, full_model)
print(comparison)

# for the GAM-based circular graphs see the additional separate code in Python.

```


<a name="S5"></a>
&nbsp;

**5. Comparison of distance error between cardiac phases (individual animals)** 

```{r}

###5.1. Item-by-item comparisons

# prepare data
d <- data[data$c_phase == "systole" | data$c_phase == "diastole", ]

d <- d %>% 
  dplyr::group_by(ID, Stimulus, c_phase) %>%
  dplyr::summarize(distance_error = mean(DistanceError))

d <- spread(d, key = Stimulus, value = distance_error)

d <- pivot_wider(d, names_from = c(c_phase), values_from = c(Scorpio, Crocodile, FinalSnake, FinalWolf, Deer, Pig, Turtle, Rabbit))


## Threatening

# Scorpio
shapiro.test(d$Scorpio_diastole)
shapiro.test(d$Scorpio_systole)
t.test(d$Scorpio_systole, d$Scorpio_diastole, paired = T)

# Wolf
shapiro.test(d$FinalWolf_diastole)
shapiro.test(d$FinalWolf_systole)
wilcox.test(d$FinalWolf_systole, d$FinalWolf_diastole, paired = T)

# Snake
shapiro.test(d$FinalSnake_diastole)
shapiro.test(d$FinalSnake_systole)
t.test(d$FinalSnake_systole, d$FinalSnake_diastole, paired = T)

# Crocodile
shapiro.test(d$Crocodile_diastole)
shapiro.test(d$Crocodile_systole)
t.test(d$Crocodile_systole, d$Crocodile_diastole, paired = T)


# prepare graphics
par(mfrow=c(1,4))
c_threat_sys <- "#6c030f"
c_threat_dias <- "#af7d81"

boxplot(d$Crocodile_systole, d$Crocodile_diastole, col = c(c_threat_sys, c_threat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Crocodile")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


boxplot(d$FinalWolf_systole, d$FinalWolf_diastole, col = c(c_threat_sys, c_threat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Wolf")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


boxplot(d$FinalSnake_systole, d$FinalSnake_diastole, col = c(c_threat_sys, c_threat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Snake")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


boxplot(d$Scorpio_systole, d$Scorpio_diastole, col = c(c_threat_sys, c_threat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Scorpio")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)
# export 3 x 7.5 cm


## Non-threatening

# Deer
shapiro.test(d$Deer_diastole)
shapiro.test(d$Deer_systole)
wilcox.test(d$Deer_systole, d$Deer_diastole, paired = T)

# Turtle
shapiro.test(d$Turtle_diastole)
shapiro.test(d$Turtle_systole)
t.test(d$Turtle_systole, d$Turtle_diastole, paired = T)

# Pig
shapiro.test(d$Pig_diastole)
shapiro.test(d$Pig_systole)
t.test(d$Pig_systole, d$Pig_diastole, paired = T)

# Rabbit
shapiro.test(d$Rabbit_diastole)
shapiro.test(d$Rabbit_systole)
t.test(d$Rabbit_systole, d$Rabbit_diastole, paired = T)

# prepare graphics
par(mfrow=c(1,4))
c_nonthreat_sys <- darken(rgb(10/255, 80/255, 200/255),0.55)
c_nonthreat_dias <- "#9590a8"

boxplot(d$Deer_systole, d$Deer_diastole, col = c(c_nonthreat_sys, c_nonthreat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Deer")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


boxplot(d$Pig_systole, d$Pig_diastole, col = c(c_nonthreat_sys, c_nonthreat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Pig")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


boxplot(d$Turtle_systole, d$Turtle_diastole, col = c(c_nonthreat_sys, c_nonthreat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Turtle")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)


boxplot(d$Rabbit_systole, d$Rabbit_diastole, col = c(c_nonthreat_sys, c_nonthreat_dias), names = c("Systole", "Diastole"), frame = FALSE, notch = TRUE, ylab = "Distance Error", cex.lab = 1.4, cex.axis = 1, ylim = c(-80,80), main = "Rabbit")
abline(h=0, col="gray20", lwd = 1.3, lty = 2)
# export 3 x 7.5 cm

```


<a name="S6"></a>
&nbsp;

**6. Distance errors as a function of true distance (individual animals)** 

```{r}

## Threatening animals

# prepare data
d <- data[data$c_phase == "systole" | data$c_phase == "diastole", ]
d <- d[d$FearObject == "True",]

# prepare graphics
c_threat_sys <- "#6c030f"
c_threat_dias <- "#af7d81"
bold.text <- element_text(face = "bold", color = "black")

# plot the resuls for different animals
for (p in unique(d$Stimulus)) {

subdata <- d[d$Stimulus == p,]

Figure <- ggplot(data = subdata, aes(x = RealDistance, y = DistanceError, color = c_phase)) + geom_smooth(method = "loess", level=0.95, alpha = 0.5, aes(fill=c_phase)) +
  labs(y = "Distance Error", x = "True Distance") +
  ggtitle(p) + scale_color_manual(values = c('systole' = c_threat_sys, 'diastole' = c_threat_dias)) + scale_fill_manual(values = c('systole' = c_threat_sys, 'diastole' = c_threat_dias)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 17), axis.text=element_text(size=17),  axis.title=element_text(size=18)) +
  scale_x_continuous(limits= c(min(data$RealDistance), max(data$RealDistance)), expand = c(0.01,0.01)) + coord_cartesian(ylim=c(-50, 50)) + theme(axis.title = bold.text, axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), axis.title.x =   element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

plot(Figure)
}

## Non-threatening animals

# prepare data
d <- data[data$c_phase == "systole" | data$c_phase == "diastole", ]
d <- d[d$FearObject == "False",]

# prepare graphics 
c_nonthreat_sys <- darken(rgb(10/255, 80/255, 200/255),0.55)
c_nonthreat_dias <- "#9590a8"

# plot the results for different animals
for (p in unique(d$Stimulus)) {

subdata <- d[d$Stimulus == p,]

Figure <- ggplot(data = subdata, aes(x = RealDistance, y = DistanceError, color = c_phase)) + geom_smooth(method = "loess", level=0.95, alpha = 0.5, aes(fill=c_phase)) +
  labs(y = "Distance Error", x = "True Distance") +
  ggtitle(p) + scale_color_manual(values = c('systole' = c_nonthreat_sys, 'diastole' = c_nonthreat_dias)) + scale_fill_manual(values = c('systole' = c_nonthreat_sys, 'diastole' = c_nonthreat_dias)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 17), axis.text=element_text(size=17),  axis.title=element_text(size=18)) +
  scale_x_continuous(limits= c(min(data$RealDistance), max(data$RealDistance)), expand = c(0.01,0.01)) + coord_cartesian(ylim=c(-50, 50)) + theme(axis.title = bold.text, axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), axis.title.x =   element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

plot(Figure)
}

```


<a name="S7"></a>
&nbsp;

**7. Width of (distance & angular) error distributions as function of threat and cardiac phase** 
```{r}

# model width of distance error distributions as function of threat and cardiac phase
aov_d <- data %>% 
  filter(c_phase %in% c("diastole", "systole")) %>% 
  group_by(ID, FearObject, c_phase) %>% 
  dplyr::summarise(sd = sd(abs(DistanceError))) %>% 
  ungroup()

cat("\n\n### ANOVA – sd DISTANCE ERROR:\n")

fit_all <- aov_ez(data = aov_d,
                  dv = "sd",
                  id = "ID",
                  within=c("c_phase", "FearObject"),
                  return = afex_options("return_aov"),
                  anova_table = list(),
                  fun_aggregate = mean)
fit_all 
summary(fit_all)

print(aov_d %>% 
        group_by(FearObject) %>% 
        dplyr::summarise(mean_sd = mean(sd),
                         sd_sd = sd(sd)))


# model angular error as function of threat and cardiac phase
aov_d <- data %>% 
  filter(c_phase %in% c("diastole", "systole")) %>% 
  group_by(ID, FearObject, c_phase) %>% 
  dplyr::summarise(m = mean(abs(AngularErrorDeg)), 
                   sd = sd(AngularErrorDeg)) %>% 
  ungroup()

cat("\n\n### ANOVA – mean ANG ERROR\n")
fit_all <- aov_ez(data = aov_d,
                  dv = "m",
                  id = "ID",
                  within=c("c_phase", "FearObject"),
                  return = afex_options("return_aov"),
                  anova_table = list(),
                  fun_aggregate = mean)
fit_all 
summary(fit_all)
cat("\n\n### ANOVA – sd ANG ERROR\n")
fit_all <- aov_ez(data = aov_d,
                  dv = "sd",
                  id = "ID",
                  within=c("c_phase", "FearObject"),
                  return = afex_options("return_aov"),
                  anova_table = list(),
                  fun_aggregate = mean)
fit_all 
summary(fit_all)
print(aov_d %>% 
        group_by(FearObject) %>% 
        dplyr::summarise(grand_m = mean(m), 
                         grand_sd = sd(m),
                         mean_sd = mean(sd),
                         sd_sd = sd(sd)))



```


